---
title: "Prior-post"
output: html_notebook
---

LA start of Rmd with prior post checks, to be finished 

run after fitting models 
```{r}
library(bayesplot)
```

# splines 

usage: invlogit transform to get between 0 and 10 for earlier coefficients, then between 0 and 1.15 
## no shocks
```{r}
parname <- "a_sigma" 
samp <- fit$samples$draws(parname )
#mcmc_trace(samp)
mcmc_dens_overlay(samp)
```
prior was half-standard normal, seems quite constrained for low splines index...
but possibly also the last one? 
 
```{r}
parname <- "a_mu" 
samp <- fit$samples$draws(parname )
#mcmc_trace(samp)
mcmc_dens_overlay(samp)
```
st normal on a_mu too constrained...

note differences in a_mu
- st normal in no shocks
- n(0,3) in shocks 2


# shocks 
```{r}
parname <- "a_sigma" 
samp <- fits$fit[[1]]$samples$draws(parname )
#mcmc_trace(samp)
mcmc_dens_overlay(samp)
```



    
```{r}
parname <- "a_mu" 
samp <- fits$fit[[1]]$samples$draws(parname )
#mcmc_trace(samp)
mcmc_dens_overlay(samp)
```

    
